The effects of night-life on subsequent day sporting performance

### 2017-07-03 poster/poster.tex
Centered 'model' block.
Fixed formatting.

\documentclass[24pt, a0paper, portrait]{tikzposter} 
 \usepackage{algorithm2e} \usepackage{amsmath} \usepackage{amsthm} \usepackage{amsfonts} \usepackage{bbm} \usepackage{color,soul} \usepackage{framed} \usepackage{hyperref} \usepackage{mathtools} \usepackage[utf8]{inputenc} 
\usepackage{subcaption}
 \newtheorem{theorem}{Theorem}[section] \newtheorem{lemma}[theorem]{Lemma} \newtheorem{proposition}[theorem]{Proposition} \newtheorem{corollary}[theorem]{Corollary}  \DeclareMathOperator*{\argmin}{arg\,min} \DeclareMathOperator*{\argmax}{arg\,max} \newcommand{\D}{\mathrm{d}} \SetKwInput{KwInput}{Input} \SetKwInput{KwOutput}{Output}   \title{The effects of night-life on subsequent day sporting performance} \author{Eric Lax, Andreas Santucci} \date{May 19th, 2017} \institute{Institute for Computational and Mathematical Engineering}   \usetheme{Board}   \begin{document}   \maketitle

@@

\block{Model}{
  \[
    \texttt{meet spread} \sim \texttt{party} + \substack{\texttt{days since} \\ \texttt{last game}} + \substack{\texttt{time}\\ \texttt{difference}} + \substack{\texttt{distance} \\ \texttt{traveled}}
  \]
}

>>>>

\documentclass[24pt, a0paper, portrait]{tikzposter}

\usepackage{algorithm2e} 
\usepackage{amsmath} 
\usepackage{amsthm} \usepackage{amsfonts} 
\usepackage{bbm} 
\usepackage{color,soul} \usepackage{framed} 
\usepackage{hyperref} 
\usepackage{mathtools} \usepackage[utf8]{inputenc} 
\usepackage{subcaption}

\newtheorem{theorem}{Theorem}[section] 
\newtheorem{lemma}[theorem]{Lemma} \newtheorem{proposition}[theorem]{Proposition} \newtheorem{corollary}[theorem]{Corollary}  \DeclareMathOperator*{\argmin}{arg\,min} \DeclareMathOperator*{\argmax}{arg\,max} 
\newcommand{\D}{\mathrm{d}} 
\SetKwInput{KwInput}{Input} 
\SetKwInput{KwOutput}{Output}

\title{The effects of night-life on subsequent day sporting performance} 
\author{Eric Lax, Andreas Santucci} 
\date{May 19th, 2017} 
\institute{Institute for Computational and Mathematical Engineering}   
\usetheme{Board}

\begin{document}

\maketitle

@@

\begin{columns}

\column{0.2}
\column{0.6}

\block{Model}{
  \[
    \texttt{meet spread} \sim \texttt{party} + \substack{\texttt{days since} \\ \texttt{last game}} + \substack{\texttt{time}\\ \texttt{difference}} + \substack{\texttt{distance} \\ \texttt{traveled}}
  \]
}
\column{0.2}
\end{columns}
